---
title: "Lab5"
author: "Bek"
date: "`r Sys.Date()`"
output: 
  html_document:
    toc: yes
    toc_float: yes
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```

# Tasks 

## Task1

```{r}
getwd()
```


## Task2

### simulate a binomial experiment where n=10,p=0.7, and Y=number of successes. For 100, 200, 500, 1000, 10000 iterations

```{r}
library(MATH4753LAB5)

mybin(iter = 100, n=10, p = 0.7)
mybin(iter = 200, n=10, p = 0.7)
mybin(iter = 500, n=10, p = 0.7)
mybin(iter = 1000, n=10, p = 0.7)
mybin(iter = 10000, n=10, p = 0.7)

```

### For the last simulation (10,000 iterations) copy and paste the table that is produced from the function.

     0      1      2      3      4      5      6      7      8      9     10 
0.0000 0.0000 0.0022 0.0087 0.0395 0.1016 0.1961 0.2741 0.2268 0.1262 0.0248 

```{r}
dbinom(0, 10, 0.7)
dbinom(1, 10, 0.7)
dbinom(2, 10, 0.7)
dbinom(3, 10, 0.7)
dbinom(4, 10, 0.7)
dbinom(5, 10, 0.7)
dbinom(6, 10, 0.7)
dbinom(7, 10, 0.7)
dbinom(9, 10, 0.7)
dbinom(9, 10, 0.7)
dbinom(10, 10, 0.7)
```

The answers using dbinom differs from the simulations, probably because dbinom gives expected answers. Therefore, the larger the iteration, the more the simulation values get closer to expected values.


## Task3 

### Suppose that there is a bag of 20 marbles, 12 white (“1”) and 8 black “0”

###	Use the function myhyper(), on CANVAS, assume Y = number of whites, remember sampling is without replacement, n=5. 

### Use this code to make barplots of Y for the following number of iterations	100, 200, 500, 1000, 10000




```{r}
marbles = c(1, 1, 1, 1, 1, 1, 1, 1, 1, 1, 1, 1, 0, 0, 0, 0, 0, 0, 0, 0)
sample(marbles, 5, replace = FALSE)
sample(marbles, 5, replace = TRUE)
myhyper(iter=100, N = 20, r = 12, n =5)
myhyper(iter=200, N = 20, r = 12, n =5)
myhyper(iter=500, N = 20, r = 12, n =5)
myhyper(iter=1000, N = 20, r = 12, n =5)
myhyper(iter=10000, N = 20, r = 12, n =5)




```

### For the last simulation (10,000 iterations) copy and paste the table that is produced from the function.

     0      1      2      3      4      5 
0.0042 0.0489 0.2446 0.3897 0.2627 0.0499 

```{r}
round(dhyper(0:5, m=12, n=8,k=5), 4)

```

dhyper results are very close to myhyper results



## Task4

### In lab5.r there is a function called mysample(). Look at the code and describe what you think it should do – record your response here.

It will probably draw a barplot consisting of multiple samples


### Run the function with the following arguments mysample(n=1000, iter=30,time=1)

mysample(n = 1000, iter = 30, time = 1)



It displays barplots with replacement that display iterations from 1 to 30 that were selected from 1 to 10.

```{r}
mysample(n = 1000, iter = 1, time = 1)
```


## Task5 

###	Use R to calculate,  (■(8@4)) – hint: Try choose(), 	P(Y>4),Y~Pois(λ=2)

```{r}
choose(8,4)
1-ppois(4, lambda = 2)
```

### Some more calculations in R

	P(Y=10),Y~NegBin(p=0.4,r=3) see CANVAS which has a full explanation of this.
	P(Y≤8),Y~Bin(n=15,p=0.4)


```{r}
dnbinom(7,3,0.4)

mynbin=function(y,r,p){
  
  choose(y-1,r-1)*p^r*(1-p)^(y-r)
}

mynbin(10,3,0.4)
pbinom(8,size = 15,p=0.4)
```

## Task6

```{r}
MATH4753LAB5::mybin(iter=1000,n=18, p=0.3)
```






